Trends from 30-year observations of downward solar irradiance in Thessaloniki, Greece

### 2023-12-07 MDPI_submission.Rmd
Commit 2023-12-07 11:10

spp$cor.df             <- NULL
spp$cor.null_value     <- NULL
spp$cor.alternative    <- NULL
spp$cor.method         <- NULL
spp$cor.data_name      <- NULL
spp$cor.p              <- NULL
spp$cor.conf.level     <- NULL
spp$cor.conf_int_1     <- NULL
spp$cor.conf_int_2     <- NULL

>>>>

spp$cor.df             <- NULL
spp$cor.null_value     <- NULL
spp$cor.alternative    <- NULL
spp$cor.method         <- NULL
spp$cor.data_name      <- NULL
spp$cor.p              <- NULL
spp$cor.conf.level     <- NULL
spp$cor.conf_int_1     <- NULL
spp$cor.conf_int_2     <- NULL
spp$cor.conf_level     <- NULL
